Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-25 paper.tex
Added figures about ALS of all methods and ALS+Bias of three methods

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

The number of files selected for every subject is randomly selected in 
a uniform distribution with parameters \textit{\textbf{a}} and 
\textit{\textbf{b}} where \textit{\textbf{b}} is set to the total 
number of files $N_{f}$ and \textit{\textbf{a}} is set such that the 
distribution average equals to $\alpha N_{f}$ where $\alpha$ is the training ratio,  that is, 
$\textit{\textbf{a}}=(2\alpha-1)N_{f}$. \todo{Explain what you do when alpha is lower than 0.5}

This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected in every subject is randomly selected in a triangular distribution
with parameters a, b and c where a, b and c are set as follows: \ldots{}
This distribution aims at sampling files produced towards the end of the execution.
Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a (RFNT-L):  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
than the two first generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.

\item Smallest-a (RNFT-S): In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}

@@

\todo{1. Use the same ordering and paragraph headings as in the method 
section. 2. Don't mix multiple ideas/results in the same paragraph. 3. 
Mention and describe the figure before discussing it.}

Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.5\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.5\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.5\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}
In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the accuracy graph of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}

@@

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
        \end{subfigure}
	\caption{Average performance of Complete Columns methods in three different condition pairs}
	\label{fig:simple-methods}
\end{figure}

% Present your results: accuracy, ROC curves, transparency matrix, factors.

>>>>

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

@@

The number of files selected for every subject is randomly selected in
a uniform distribution $U(\textit{a},\textit{b})$, where \textit{\textbf{b}} is set to the total
number of files $N_{f}$ and \textit{\textbf{a}} is set according to training ratio ($\alpha$) as follow:

\[
  \begin{cases}
          \textit{\textbf{a}} = 0      & \text{if $\alpha \leq 0.5$ }\\

          \textit{\textbf{a}} = (2\alpha - 1) N_{f} & \text{if $\alpha > 0.5$}
  \end{cases}
\]

This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.\\

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected for every subject is randomly selected in
a triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the other two parameters could be set according to two different approaches. By considering $\alpha$ as training ratio, the distribution average equals to $\alpha N_{f}$ which that means f  $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would get a negative value in this regard, therefore to avoid this issue the uniform distribution is applied for $\alpha < \nicefrac{1}{3}$. But for $\alpha \leq \nicefrac{1}{3}$ the following approaches are applicable.

 \ldots{}
This distribution aims at sampling files produced towards the end of the execution.
Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a (RFNT-L):  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
than the two first generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.

\item Smallest-a (RFNT-S): In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}

@@

\todo{1. Use the same ordering and paragraph headings as in the method 
section. 2. Don't mix multiple ideas/results in the same paragraph. 3. 
Mention and describe the figure before discussing it.}
\subsubsection{Random Unreal}
Figure~\ref{fig:unreal method} represents
the accuracy graph of Complete Columns method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of Random Unreal methods in three different condition pairs}
        \label{fig:unreal method}
\end{figure}
\subsubsection{Complete Columns}
Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}
\subsubsection{Complete Rows}
Figure~\ref{fig:rows method} represents
the accuracy graph of Complete Rows method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of Complete Rows methods in three different condition pairs}
        \label{fig:rows method}
\end{figure}
\subsubsection{Random Subjects-RS}
Figure~\ref{fig:RS method} represents
the accuracy graph of RS method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of Complete RS methods in three different condition pairs}
        \label{fig:RS method}
\end{figure}
\subsubsection{RandomFile Numbers(Uniform) - RFNU}
Figure~\ref{fig:RFNU method} represents
the accuracy graph of RFNU method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:RFNU method}
\end{figure}
\subsubsection{RNFT-L}
Figure~\ref{fig:RFNT-L method} represents
the accuracy graph of RFNT-L method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-L methods in three different condition pairs}
        \label{fig:RFNT-L method}
\end{figure}
\subsubsection{RFNT-S}
Figure~\ref{fig:RFNT-S method} represents
the accuracy graph of RFNTS method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-S methods in three different condition pairs}
        \label{fig:RFNT-S method}
\end{figure}
% General conclution on results of ALS without Bias 
Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the accuracy graph of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.\\

In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the accuracy graph of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}

@@

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
        \end{subfigure}
	\caption{Average performance of Complete Columns methods in three different condition pairs}
	\label{fig:simple-methods}
\end{figure}
%-----------------------------------------------------------
\subsection{ALS with biases}

\subsubsection{RandomFile Numbers(Uniform) - RFNU}
Figure~\ref{fig:RFNU method} represents
the accuracy graph of RFNU method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:RFNU method}
\end{figure}
\subsubsection{RNFT-L}
Figure~\ref{fig:RFNT-L method} represents
the accuracy graph of RFNT-L method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-L methods in three different condition pairs}
        \label{fig:RFNT-L method}
\end{figure}
\subsubsection{RFNT-S}
Figure~\ref{fig:RFNT-S method} represents
the accuracy graph of RFNTS method with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of RFNT-S methods in three different condition pairs}
        \label{fig:RFNT-S method}
\end{figure}
%-----------------------------------------------------------
% Present your results: accuracy, ROC curves, transparency matrix, factors.
